\documentclass{resume}

\begin{document}

\namesection{Nick Spinale}{
  \href{http://nickspinale.com}{nickspinale.com}
  | \href{mailto:nick@nickspinale.com}{nick@nickspinale.com}
  | \href{https://github.com/nspin}{github.com/nspin}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Carleton College}
\descript{Math/Computer Science}
\location{Sep 2014 – June 2018 | Northfield, MN}
\location{GPA: 3.8}
Phi Beta Kappa \\
{\descript{Selected Courses}}
Topics in Abstract Algebra \\
Topics in Elliptic Curves \\
Programming Languages \\
Computer Architecture \\
Operating Systems \\
Data Mining \\
Probability Theory \\
Statistical Inference \\
% Software Development \\
Multivariable Calculus \\
Quantum Computing \\
\sectionsep

\subsection{Reni Institute}
\descript{Mathematics}
\location{Aug – Dec 2016 | Budapest, Hungary}
\location{GPA: 4.0}
{\descript{Courses}}
Mathematical Cryptography \\
Theory of Computing \\
Number Theory \\
Graph Theory \\
Set Theory \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Languages}
\metanote{Most Comfortable:}
Haskell \sep
C \sep
Python \sep
Go \\
Shell \sep
Java \sep
JavaScript \sep
TeX \\
\metanote{Comfortable}
OCaml \sep
Coq \sep
Rust \sep
C++ \\
Scheme \sep
SQL \sep
HTML/CSS \\
ASM (x86, ARM, MIPS) \sep
R \\
\metanote{Familiar:}
Ruby \sep Magma \sep Mathematica \\
\sectionsep

\subsection{Systems and Tools}
Unix-like environments \sep Git \\
GDB \sep Ghidra \sep IDA Pro \\
AWS \sep Kubernetes \sep Docker \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
\begin{tabular}{cl}
  \color{subheadings}\selectfont\faGlobe & \href{http://nickspinale.com}{nickspinale.com} \\
  \color{subheadings}\selectfont\faEnvelope & \href{mailto:nick@nickspinale.com}{nick@nickspinale.com} \\
  \color{subheadings}\selectfont\faLinkedin & \href{https://www.linkedin.com/in/nickspinale}{linkedin.com/in/nickspinale} \\
  \color{subheadings}\selectfont\faGithub & \href{https://github.com/nspin}{github.com/nspin} \\
  \color{subheadings}\selectfont\faTwitter & \href{https://twitter.com/nick\_spinale}{nick\_spinale} \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Arm Research}
\descript{| Research Engineer }
\location{October 2018 – Present | Cambridge, UK}
\vspace{1.25\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Design, propose, and execute research projects involving privacy, confidential computing, trusted execution environments, operating systems, and virtualization.
\end{tightemize}
\sectionsep

\runsubsection{Google}
\descript{| Software Engineering Intern }
\location{June – September 2017 | Sunnyvale, CA}
% \vspace{1.25\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Collaborated with a number of teams, both internal and external (including Istio and SPIFFE), to push the state of the art of security within service-oriented systems towards mTLS-everywhere.
\item Developed a system for securely bootstrapping and managing service identities within the Google Cloud Edge infrastructure.
\end{tightemize}
\sectionsep

\runsubsection{Carve Systems, LLC}
\descript{| HackNY Fellow + Intern }
\location{June – December 2016 | New York, NY}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Conducted penetration tests on client systems and products.
\item Built tools for discovering vulnerabilities in a variety of systems.
\item Maintained servers and services for simulating attacks and streamlining the security assessment and reporting process.
\end{tightemize}
\sectionsep

\runsubsection{Datrium, Inc}
\descript{| Software Engineering Extern }
\location{December 2015 | Sunnyvale, CA}
\begin{tightemize}
\item Collaborated with a team of senior engineers and researchers on a cutting-edge virtualized storage system.
\item Built a set of utilities for deserializing intermediate data from a long-running space reclamation process.
\end{tightemize}
\sectionsep

\runsubsection{Carleton College}
\descript{| Computer Science Lab Assistant}
\location{September 2015 – Present | Northfield, MN}
\begin{tightemize}
\item Aid fellow Computer Science students in developing problem solving skills and algorithmic intuition.
\item Identify, explain, and help correct bugs in students’ Python, Java, C, MIPS, and Scheme programs.
\end{tightemize}
\sectionsep

\runsubsection{Pismo Investments}
\descript{| Software Engineering Intern}
\location{June – September 2015 | Waltham, MA}
\begin{tightemize}
\item Contributed to the schematics of an inference engine for modeling and analyzing corporate structure.
\item Built and maintained an Enterprise Java backend that interfaced with a relational database and exposed a REST API.
\item Designed a web application using Angular.js that demonstrated Pismo's product's modeling capabilities to potential investors.
\end{tightemize}
\sectionsep

% \runsubsection{Colegio Salesiano Don Bosco}
% \descript{| English Teacher}
% \location{May – July 2014 | Masaya, Nicaragua}
% \begin{tightemize}
% \item Taught English classes of up to fifty students from grades four through six in an economically struggling neighborhood.
% \item Organized, advertised, and led language exchange groups open to the public.
% \item Assisted in teaching upper-level English to high school students and adults.
% \end{tightemize}
% \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\begin{tabular}{rll}
  2014 & U.S. Presidential Scholar & U.S. Department of Education \\
  2016 & HackNY Fellow & \href{https://apply.hackny.org}{HackNY} \\
  2018 & \href{https://apps.carleton.edu/curricular/cs/major/awards/pollatsek/}{David Pollatsek Prize in Computer Science} & Carleton College \\
\end{tabular}
\sectionsep

\end{minipage}
\end{document}
